---
author: "Jessica Cheng"
date: "2023-12-04"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
## Q1 (Matching): 

In online retailing, Directed Search indicates when users search for a specific product
name to purchase a product. On the other hand, undirected search indicates when a user stumbles upon
a product to purchase.
To examine if direct or undirected search increases sales, an analyst examines user activity from the
website of an online retailer. The data set is developed from cookies that are saved on a user’s
computer along with data from the profile’s users create:

```{r,message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(MatchIt)
search_data = read.csv("matching.csv")
```

*(1) Run a naïve model where you regress sales (in $) on if the session was classified as a directed search or undirect search session. There are three metrics of the sales from a website. Examine the effect of directed sales on all three sales metrics.* 

```{r}
promote_sales = summary(lm(PromotedSales ~ DirectedSearchUsage, data = search_data))
promote_sales
```
- PromotedSales=510.17+650.20×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: 650.20, as DirectedSearchUsage increase by one unit, PromotedSales is estimated to increase by 650.20 units.

```{r}
nonpromote_sales = summary(lm(NonpromotedSales ~ DirectedSearchUsage, data = search_data))
nonpromote_sales
```
- NonpromotedSales = 152.19-66.23×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: -66.23, as DirectedSearchUsage increase by one unit, NonpromotedSales is estimated to decrease by 66.23 units.

```{r}
overall_sales = summary(lm(OverallSales ~ DirectedSearchUsage, data = search_data))
overall_sales
```
- OverallSales = 662.37+583.97×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: 583.97, as DirectedSearchUsage increase by one unit, OverallSales is estimated to increase by 583.97 units.



*Users who indulge in directed search may be systematically different from those who perform undirect search. To overcome this issue, match users on the probability that they were performing directed search. Use propensity score matching to match users on log income, Education years, number of prior sessions, days since last purchase and historical total purchases. Regress the three sales metrics on the directed sales indicator for the matched set of users. Is there any difference in your findings after matching users?* 

```{r}
# Perform PScore
PScore = glm(DirectedSearchUsage ~ log(1+Income)+Education+NumSessions
             +DaysSinceLastPurchase+HistoricalTotalPurchases,
             data = search_data, family = "binomial")$fitted.values
search_data$PScore = PScore
```

```{r}
# Perform Matching. Use the matchIT command to generate propensity scores and match
# replace=FALSE will not take into match for next round
match_output = matchit(DirectedSearchUsage ~ log(1+Income)+Education+NumSessions
                       +DaysSinceLastPurchase+HistoricalTotalPurchases,
                       data= search_data,
                       method = "nearest",
                       distance = "logit",
                       caliper = .001, #how close treatment and control need to be
                       #if increase this value we will get more matched household 
                       replace = FALSE, #match without replacement
                       ratio = 1) #one on one matching
summary(match_output)
```

- Before matching, there were imbalances in covariates, as evidenced by non-zero standardized mean differences.
- After matching, the standardized mean differences are closer to 0, indicating improved balance.

```{r}
match_data = match.data(match_output)
```

```{r}
promote_sales = summary(lm(PromotedSales ~ DirectedSearchUsage, data = match_data))
promote_sales
```
- PromotedSales = 585.05 + 450.15×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: 450.15, as DirectedSearchUsage increase by one unit, PromotedSales is estimated to increase by 450.15 units.
- The influence of directed search on sales appears to be lower in the matched data compared to the non-matched data.

```{r}
nonpromote_sales = summary(lm(NonpromotedSales ~ DirectedSearchUsage, data = match_data))
nonpromote_sales
```
- NonpromotedSales = 148.83-57.76×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: -57.76, as DirectedSearchUsage increase by one unit, NonpromotedSales is estimated to decrease by 57.76 units.
- The influence of directed search on sales appears to be lower in the matched data compared to the non-matched data.

```{r}
overall_sales = summary(lm(OverallSales ~ DirectedSearchUsage, data = match_data))
overall_sales
```
- OverallSales = 733.89+392.39×DirectedSearchUsage. The coefficent value of DirectedSearchUsage: 392.39, as DirectedSearchUsage increase by one unit, OverallSales is estimated to increase by 392.39 units.
- The influence of directed search on sales appears to be lower in the matched data compared to the non-matched data.

## Q2 (Synthetic Control): 
One of the first contexts where the synthetic control approach was developed was to understand if raising taxes on cigarette sales in California decreased sales. In this question, you are required to import data on cigarette taxes and sales. Here is what you need to do

```{r,message=FALSE, warning=FALSE}
library(tidyr)
library(glmnet)
library(janitor)
library(Synth)
library(ggthemes)
library(patchwork)
```

#### (1) Import the smoking.csv data. 
```{r}
smoke_data = read.csv("smoking.csv")
smoke_data <- as.data.frame(smoke_data)
```
#### (2) Create unique numeric state IDs
```{r}
smoke_data$state_id <- as.numeric(factor(smoke_data$state))
smoke_data$year <- as.numeric(smoke_data$year)
smoke_data$treat <- smoke_data$state_id == 3
```

#### (3) Use the following variables as predictors: Inincome, retprice, age15to25,beer, lagged cigertte sales from 1975, 1980, 1988
#### (4) Use data between 1970 and 1988 to create synthetic control
```{r,message=FALSE, warning=FALSE}
treatment_unit = 3
Sys.setenv(LANGUAGE = "en")
# Now we can use Synth's data preparation package. 
dataprep.out=
  dataprep(foo = smoke_data,
           dependent = "cigsale",
           unit.variable = "state_id",
           time.variable = "year",
           
           predictors = c("lnincome", "retprice", "age15to24", "beer"),
           predictors.op = "mean",
           special.predictors = list(list("cigsale", 1975, "mean"), list("cigsale", 1980, "mean"), list("cigsale", 1988, "mean")),
           treatment.identifier = 3,
           
           #which panels are we using to construct the synthetic control?
           # Controls here will be every other district.!!
           controls.identifier = setdiff(unique(smoke_data$state_id), treatment_unit),

           time.predictors.prior = c(1970:1988),
           time.optimize.ssr = c(1970:1988),
           
           unit.names.variable = "state",
           time.plot = 1970:2000)
```


```{r}
synth.out = synth(dataprep.out)
```
#### (5) Using ggplot, plot the line for the actual sales in California and the synthetic control

```{r}
path.plot(dataprep.res = dataprep.out, synth.res = synth.out,Xlab="Year",Ylab="cigarette Sales",Main="Comparison of Synth vs. Actual Cum. cigarette in California")
abline(v=1988,lty=2,col="red")
```
## Q3 (Regression Discontinuity): Does the position of an online advertisement impact the number of clicks it obtains? This question can be analyzed using a regression discontinuity model. 

```{r,message=FALSE, warning=FALSE}
library(rddtools)
library(rdrobust)
library(rdd)
```

```{r}
rd_data = read.csv("rd.csv")
```

#### (1) Assign a rank to each of the bids. These ranks will be the within auction rank of the different bids. In auction id = 1, the bid with a value of 4.23 will have rank 1 (as it is the bid in the auction with the highest value), the bid with a value of 4.15 will have a value of 2, and so on.

```{r}
rd_data <- rd_data %>%
  group_by(auction_id) %>%
  arrange(desc(bid)) %>%
  mutate(rank = row_number())
```


#### (2) Limit your analysis to advertisements that have a rank of 1 or 2.

```{r}
rd_data <- rd_data %>% filter(rank %in% c(1, 2))
```

#### (3) Within each auction id, compute the difference in the bid between advertisements with rank 1 and rank 2. For example, the difference in the bid amount between advertisements with rank 1 and 2 is 0.08. The positive value of this will serve as the forcing value for the bid with rank 1 and the negative value of this will serve as the forcing value for the bid with rank 2.

```{r}
rd_data <- rd_data %>% 
  arrange(auction_id, rank) %>%
  group_by(auction_id) %>%
  mutate(z = ifelse(rank == 1, -diff(bid), diff(bid)))
rd_data <- rd_data %>%
  mutate(treat = ifelse(rank==1,1,0))
```

```{r}
ggplot(rd_data, aes(y=ctr,x=z)) + 
  geom_point(aes(color = rank+1),show.legend = FALSE) + 
  geom_vline(xintercept = 0, linetype="dashed", color="red") +
  geom_smooth(aes(group = factor(rank), color = rank), method = "lm", show.legend=FALSE)
```

#### Use this dataset to examine how click through rates differ for advertisements for rank 1 and 2 using a regression discontinuity framework. The value of the cutoff will be 0 in this case.
```{r}
# naive rdd without bandwidth
summary(lm(ctr ~ treat+z, data=rd_data))
```
- Use naive linear regression, including the confound variable z, ranking in the first place increase average 19% in click through rate.

```{r}
## Use rdrobust to find out the bandwidth
rd_robust_rdd = rdrobust(rd_data$ctr, rd_data$z, c=0)
summary(rd_robust_rdd)
rdplot(rd_data$ctr, rd_data$z, c=0)
```
- Use built-in package to find out the bandwidth and coefficient. Here, ranking in the first place increase average 18% in click through rate.

```{r}
rd_2 = rd_data %>% filter(z >= -0.339 & z <= 0.339)

ggplot(rd_2, aes(y=ctr,x=z)) + 
  geom_point(aes(color = rank+1), show.legend = FALSE) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  geom_smooth(aes(group = factor(rank), color = rank), method = "lm", show.legend=FALSE)
```


```{r}
# try considering polynomial trend
summary(lm(ctr ~ treat+z+z_sq, data=rd_2 %>% mutate(z_sq = z*z)))
```

```{r}
# try considering different slopes below vs. above the threshold
summary(lm(ctr ~ treat*z, data=rd_2 %>% mutate(z_sq = z*z)))
```

*Conclusion: The effect of the rank on click through rate. Compared to rank in the second place, rank in the first place increase about 18% click through rate.*
